Temperature Measurements in Optical Tweezer Experiments

### 2017-01-05 doc/draft1.tex
more drafting, more images

pressure medium. The particles of this pressure medium flow into the simulation from an outside box, whose geometry is based on the form of the object
of interest. This barostat also acts as a thermostat and thus is suitable for the application in this thesis.\\

@@

    U(r) = \frac{1}{r^{12}}

@@

in reduced units. \\
BLABLABLA\\

@@

            P_\text{ins} = e^{-\frac{U}{k_BT}} < 1

@@

        \includegraphics[scale=0.8]{images/gas_volume.pdf}
        \caption{Schematic setup for the barostat: The gas particles will be created on the face of the cube surrounding the crystal. The
                    cube is chosen to be at a distance of one side length of the nano crystal.}

@@

\newpage
\section{Results}
% results with different parameters, graphs, etc.

>>>>

pressure medium. The particles of this pressure medium flow into the simulation from an outside volume, whose geometry is based on the form of the
object of interest (this will be referred to as the minimal volume of cells). This barostat also acts as a thermostat and thus is suitable for the 
application in this thesis.\\

@@

    U(r) = \varepsilon \left(\frac{\sigma}{r}\right)^{12}

@@

where $\varepsilon$ is the interaction strength and $\sigma$ is the interaction range and $r$ is the distance between the gas particle and the
interacting particle. The gas particles do not interact with one another in this model.\\
In order to increase the efficiency of the computing process, $\sigma$ should be chosen carefully. For larger $\sigma$, the number of interaction
partners increases, which increases the number of force calculations which are a very time consuming part. For smaller $\sigma$ the possibility for
gas particles reaching the inside of the nano crystal increases, which is not desirable. So $\sigma$ should be chosen small enough to keep the force
calculations at a minimum and large enough for the particle to stay on the outside of the crystal.\\ 

@@

            P_\text{ins} = e^{-\frac{U}{k_BT}}

@@

        \includegraphics[scale=0.5]{images/gas_volume_ver2.pdf}
        \caption{Schematic setup for the barostat. The outer volume (blue) is one side length $L$ away from the nano crystal (black). 
                    The gas particles are created along the blue lines of the outer volume. Since the geometry of the nano crystal does not change, 
                    the geometry of the outer volume will be constant throughout the simulation.}

@@

\newpage
\section{Results}
% results with different parameters, graphs, etc.
Since the simulation consists of various parts that have to work together, we first need to check if every part itself works.\\
The first element of the simulation is the setup of the FCC lattice on which the particles are placed on. To check if this is done correctly, we can
use a visualisation and rendering software such as VMD\cite{Humphrey1996} or OVITO\cite{Stukowski2010}. The rendered image of the nano crystal can be
seen in fig.~\ref{fig:glass}.
\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.2]{images/initial_position_red.png}
        \caption{}
        \label{fig:gascube}
    \end{center}
\end{figure}
